Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-11-23 paper/paper.tex
Show GC model at t=1000
WIP before switching to PC
WIP

% The chemo manipulations figure is made up from 4 figures generated with
% graph_layout::g
%
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot90_fig4row1.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot180_fig4row2.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecswap_fig4row3.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_retablat_fig4row4.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecablat_fig4row5.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_mismatch_fig4row6.json
%
\begin{figure}
\includegraphics[width=0.95\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. \textbf{A} 90 degree
rotation. textbf{B} 180 degree rotation. \textbf{C} Graft swap. \textbf{D}
Retinal ablation \textbf{E} Tectal ablation \textbf{F} mismatch ablation}
\label{f:chsurg}
\end{figure}

@@

The model defined by the receptor and ligand expressions of Eqs.\,\ref{e:retrcpt}
\& \ref{e:tecligexp} along with Eq.\,\ref{e:mv2} with $m_{\!_I}=m_{\!_J}=0$ has three
free parameters; $m_{\!_G}$, $m_c$ and $r_c$. To find the best combination of
these parameters, we reasoned that evolution would optimize the arrangement of
the wildtype pattern. We performed a simulated annealing optimization to
minimize the error metric, $\epsilon$, for the wildtype pattern
(Fig.\,\ref{f:ch}E) at simulation time 1000. The parameters returned were
$m_c$ = 0.09959, $m_{\!_G}$ = 0.003841 and $r_c$ =
0.39918. Fig.\,\ref{f:nonexistent_yet} shows the $\mathbf{GC}$ simulation with
these parameters.

@@

@@

>>>>

% The chemo manipulations figure is made up from 4 figures generated with
% graph_layout::g
%
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot90_fig4row1.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecrot180_fig4row2.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecswap_fig4row3.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_retablat_fig4row4.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_tecablat_fig4row5.json
% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_mismatch_fig4row6.json
%
% (see scripts/fig_G_surgical.sh)
\begin{figure}
\includegraphics[width=0.95\linewidth]{./images/fig_chemo_manipulations.png}
\caption{Surgical manipulations in the chemoaffinity-only model. \textbf{A} 90 degree
rotation. textbf{B} 180 degree rotation. \textbf{C} Graft swap. \textbf{D}
Retinal ablation \textbf{E} Tectal ablation \textbf{F} mismatch ablation}
\label{f:chsurg}
\end{figure}

@@

% ./build/sim/agent/agent1 configs/simpler/m_ee_GC_best_1.json configs/simpler/e_wt_figcomp1.json
\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_GC_best_1_wt_figcomp1.png}
\caption{$\mathbf{GC}$ model}
\label{f:GC}
\end{figure}

The model defined by the receptor and ligand expressions of Eqs.\,\ref{e:retrcpt}
\& \ref{e:tecligexp} along with Eq.\,\ref{e:mv2} with $m_{\!_I}=m_{\!_J}=0$ has three
free parameters; $m_{\!_G}$, $m_c$ and $r_c$. To find the best combination of
these parameters, we reasoned that evolution would optimize the arrangement of
the wildtype pattern. We performed a simulated annealing optimization to
minimize the error metric, $\epsilon$, for the wildtype pattern
(Fig.\,\ref{f:ch}E) at simulation time 1000. The parameters returned were
$m_{\!_G}$ = 0.003841, $m_c$ = 0.09959 and $r_c$ = 0.39918. Fig.\,\ref{f:GC}
shows the $\mathbf{GC}$ simulation with these parameters.

@@

% ./build/sim/agent/agent1 configs/simpler/m_ee_GI_best_1.json configs/simpler/e_wt_figcomp2.json
\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_GI_best_1_wt_figcomp2.png}
\caption{$\mathbf{GI}$ model}
\label{f:GI}
\end{figure}

@@

% ./build/sim/agent/agent1 configs/simpler/m_ee_GJ_best_1.json configs/simpler/e_wt_figcomp3.json
\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_ee_GJ_best_1_wt_figcomp3.png}
\caption{$\mathbf{GJ}$ model}
\label{f:GJ}
\end{figure}
